19Q1

### 2019-04-24 19Q1.Rmd
Wilcoxon tests for CRISPR, CCLE, and CTRP

```{r, eval=FALSE}
ccle <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
# ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
gdsc <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
ccle_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
# ctrp_ptmuts <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
gdsc_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")

@@

ccle_signif_gene <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = "Gene", outfile = "./data_munging/rds/ccle_signif_g2p_gene.rds")
ccle_signif_lineage <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/ccle_signif_g2p_lineage.rds")
```

>>>>

```{r, eval=TRUE}
ccle <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
# ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
gdsc <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
ccle_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
# ctrp_ptmuts <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
gdsc_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")

@@

ccle_signif_gene <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/ccle_signif_g2p_gene.rds")
ccle_signif_gene$G2P_Drug_Gene <- ifelse(ccle_signif_gene$Drug_Gene %in% g2p_druggenes, TRUE, FALSE)
ccle_signif_lineage <- WilcoxonTestDF(dataframe = filter(ccle_ptmuts, Drug_Gene_Lin %in% g2p_dgls), grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ccle_signif_g2p_lineage.rds")

# ctrp_signif_gene <- WilcoxonTestDF(dataframe = ctrp_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/ctrp_signif_g2p_gene.rds")
# ctrp_signif_gene$G2P_Drug_Gene <- ifelse(ctrp_signif_gene$Drug_Gene %in% g2p_druggenes, TRUE, FALSE)
# ctrp_signif_lineage <- WilcoxonTestDF(dataframe = filter(ctrp_ptmuts, Drug_Gene_Lin %in% g2p_dgls), grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ctrp_signif_g2p_lineage.rds")

gdsc_signif_gene <- WilcoxonTestDF(dataframe = gdsc_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/gdsc_signif_g2p_gene.rds")
gdsc_signif_gene$G2P_Drug_Gene <- ifelse(gdsc_signif_gene$Drug_Gene %in% g2p_druggenes, TRUE, FALSE)
gdsc_signif_lineage <- WilcoxonTestDF(dataframe = filter(gdsc_ptmuts, Drug_Gene_Lin %in% g2p_dgls), grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
```

```{r}
test <- gdsc_ptmuts %>% count(Drug_Gene_Lin, Mutation_Status)
```
